A survey of HTTP caching options on the open Web

### 2014-12-16 sanity/paper1.tex
some on methodology
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@902 43ef1190-90fd-4dd7-a769-d0121f02b80e

Caching, as defined in RFC7234, requires that the server declares how
long into the future it expects the information resource in the
response to remain valid. Based on this, the client need not contact
the server at all to reuse a cached response, but this requires a
commitment from the content provider. The standard also gives the
client an opportunity to heuristically determine a time to
live. RFC7232, on the other hand, defines a protocol for asking the
server if the cached response is still fresh using conditional
requests. This doesn't burden the content provider with the task of
estimating the time to live beforehand, but then, it must be able to
answer if the resource has changed less expensively than serving the
entire response. These two approaches can be combined, as a client may
ask if a response is fresh after it has expired.

@@

>>>>

Caching, as defined in RFC7234, requires that the server declares how
long into the future it expects the information resource in the
response to remain fresh, i.e. how long it is permissible to use
it. Based on this, the client need not contact the server at all to
reuse a cached response, but this requires a commitment from the
content provider. The standard also gives the client an opportunity to
heuristically determine a time to live. RFC7232, on the other hand,
defines a protocol for asking the server if the cached response is
still fresh using conditional requests. This doesn't burden the
content provider with the task of estimating the time to live
beforehand, but then, it must be able to answer if the resource has
changed less expensively than serving the entire response. These two
approaches can be combined, as a client may ask if a response is fresh
after it has expired.

@@

\section{Methodology}

We want to find information resources on the Web, and examine HTTP
headers that may allow caching. We record headers recommended by
current standards, as well as obsoleted and non-standard
headers. Additionally, we examine the triples in the returned
information resources to see if there is information there that may be
used to calculate heuristic freshness.

However, as the community has both spidered the Web as well as
recorded lists of relevant resources, we need not do that ourselves.

The SPARQLES survey\todo{ref} has recorded the availability of SPARQL
endpoints registered in the datahub.io portal, and found that many of
them have ceased to operate. We used their list of SPARQL endpoints as
of 2014-11-17, and filtered out those deemed unresponsive by
them. This resulted in a list of 312 endpoints.

To compile a list of Web ontologies, we first queried the Linked Open
Vocabularies \todo{ref} SPARQL endpoint to retrieve all registered
ontologies. Then, we took the full list of URIs registered with
prefix.cc. The assumption that they all identify an ontology is
clearly false, as we found that for example Tim Berners-Lee's FOAF
profile has a registered URI, but it is unlikely to introduce
significant bias.

Then, we retrieved the dataset of the Billion Triple Challenge
2014\todo{ref}, a 4~GTriple corpus of spidered Web data. To compile a
list of interesting candidates to further examine, we performed a
series of data reduction steps. Due to the presence of invalid RDF, we
iterated through the NQuad files on a line-by-line basis. First, we
matched each line against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework \text{RDF::Trine}\todo{footnote} was used to parse
the line. Lines that failed to parse was discarded. We have not
investigated whether this could introduce biases. Statements were then
accepted into a new NQuad file if they had a predicate that matched
the \texttt{sd:endpoint}\todo{footnote} or matched a case-insensitive
regular expression \texttt{sparql} if the subject and objects were
both resources, or the predicates \texttt{void:vocabulary},
\texttt{rdfa:vocabulary} or \texttt{api:vocabulary} \todo{footnotes
  for all}, as well as having an resource as object. Finally,
statements with the the classes \texttt{cogs:Endpoint},
\texttt{owl:Ontology} and \texttt{voaf:Vocabulary} \todo{footnotes for
  all} in the object position were also accepted. More classes and
properties were considered, but not used in the data reduction if they
did not occur in the original data.

In the next step, we filtered out statements with URIs that were
invalid or irrelevant, e.g. URIs that didn't have a scheme or where
the scheme wasn't HTTP(S), or they were referring to private IP addresses.
